models with mice

### 2024-03-25 withmice.Rmd
knitted results with mice to pdf

---
title: "models with mice"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

@@

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(Hmisc))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(naniar))
suppressPackageStartupMessages(library(mice))

@@

@@

# Plot the graph with facets for each Question
ggplot(WBques_summary, aes(x = State, y = Proportion, fill = factor(Response, levels = rev(levels_defined)))) +
  geom_bar(stat = "identity", position = "fill") +
  scale_fill_manual(values = rev(colorsequence), name = NULL) +
  facet_wrap(~ Question, scales = "free_y", ncol = 1) +
  coord_flip() +
  labs(x = "State", y = "Proportion", title = "Proportion of Responses by State for Nuclear energy related questions") +
  theme_minimal() +
  theme(
    # Increase the size of the main title
    plot.title = element_text(size = 16, face = "bold"),
    # Increase the size of the axis titles
    axis.title = element_text(size = 14),
    # Increase the size of the facet strip text
    strip.text.x = element_text(size = 12),
    # Adjust text angle for State labels if necessary
    axis.text.y = element_text(angle = 0)
  )

@@

# Print the combined plot
grid::grid.newpage()
grid::grid.draw(combined_plot)

@@

n_acceptreject<- module2 %>%
                dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")

summary(n_acceptreject)
```

@@

#str(formice)
summary(formice)

@@

sum(is.na(formice))

@@

str(kahanall)

md.pattern(kahanall) #the variables with missing values: K_SHARM K_IPROTECT K_IPRIVACY K_SPROTECT K_SLIMCHOI K_IINTRFER K_HEQUAL K_HREVDIS1

mcar_test(data=kahanall) # p values is less than 0.05 - the condition for MCAR is not met

@@

# "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SHARM_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_SHARM variable.")

#   "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_IPROTECT_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_IPROTECT variable.")

#  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SPROTECT_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_SPROTECT variable.")

#  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SLIMCHOI_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_SPROTECT variable.")

@@

mikahan

@@

print.psych(fit, sort= TRUE, cut= 0.4)

@@

print.psych(kahanfit4, sort= TRUE, cut= 0.4)

@@

@@

kahan_imp <- mice(kahanall, m =5, maxit =30,  seed = 427, print = FALSE)

kahan_imp$chainMean

@@

kahanallscores <- mice::complete(mice::mice(kahanall, m = 5, seed = 427, print = FALSE), "broad")

@@

str(kahanallscores)

@@

## corelation table
```{r}

cor(nkahanall)

#before mice 
 cor.plot(kahanall %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))

#after mice
 cor.plot(nkahanall)

cov(nkahanall)

@@

nkahanfinal %>%
  ggplot(aes(MR1, MR2))+
  geom_count(aes(color = ..n.., size = ..n..))+
  guides(color = 'legend')+
  geom_hline(yintercept=0, colour="black", lwd=0.5)+
  geom_vline(xintercept=0, colour="black", lwd=0.5)+
  labs(x = "Hierarchy -Egalitarianism", y = "Individualism - Communitarianism")+
  ylim(-2,3)+
  xlim(-2,3)+
  theme_minimal() 
```

@@

md.pattern(ecopoln) #the variables with missing values: PRIDENUCLEAR PROSPERNUCLEAR JOBSNUCLEAR HEALTHNUCLEAR BEAUTYNUCLEAR POLLUTENUCLEAR DISPLACENUCLEAR RELYNUCLEAR

mcar_test(data=ecopoln) # p values is less than 0.76 - the condition for MCAR is met

@@

# JOBSNUCLEAR
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "JOBSNUCLEAR_MAR"
MARecopol %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the JOBSNUCLEAR variable.")

# PRIDENUCLEAR
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "PRIDENUCLEAR_MAR"
MARecopol %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the PRIDENUCLEAR variable.")

@@

miecopol

@@

print.psych(ecopolfit2, sort= TRUE, cut= 0.4)

@@

## Radar map

@@

nrow(ecopolfit2$loadings)

@@

```{r, echo=FALSE, fig.width=20, fig.height=18, out.width='70', out.height='70'}
library(fmsb)

@@

```{r, echo=FALSE}
Statenacheck1 <- allformice%>%
  na.omit()%>%
  dplyr::select(State)

summary(Statenacheck1)
```

@@

nuclear_missing <- allformice %>% dplyr::select(Risky_Nuclear,Uppercaste, Male, Hindu, urban_rural, Age, State)%>%
  na.omit()

summary(nuclear_missing)

@@

summary(nuclearfinal)
summary(nuclearfinal2)
summary(nuclearfinal3)
summary(nuclearfinal4)

@@

print(aic_values)

@@

print(bic_values)

@@

cor.plot(nforcor)
```

@@

summary(nuclearinterac)

@@

# Stargazer : all LMs

@@

#cat("\\begingroup")
#cat("\\setlength{\\tabcolsep}{1pt}")
#cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4, nuclearinterac,
          title = "Table 6: 5 linear models: Perceived Risk of Nuclear Energy",
          type = "text"
)
#cat("\\endgroup")

@@

\newpage
# Paper 2

## NUCLEAR2

@@

ecopoln2 <- formice1 %>%
  dplyr::select(
    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
    RELYNUCLEAR, age, urban_rural, gender, caste, religion, State
  )

str(ecopoln2)
md.pattern(ecopoln2) #the variables with missing values:

mcar_test(data=ecopoln2)
```

### Nuclear2 : Mifa

@@

library(mifa)

miecopoln2 <- mifa(data= ecopoln2,
                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=50,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

miecopoln2

ecopolfitn2 <- psych::fa(miecopoln2$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(ecopolfitn2, sort= TRUE, cut= 0.4)

@@

ecopoln2scores <- ecopoln2scores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))

@@

### LM : Nuclear 2 and Kahan

```{r}

@@

nuclear2lm <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(nuclear2lm)

netnuclear2lm <- lm(Netben_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(netnuclear2lm)

bennuclear2lm <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(bennuclear2lm)

@@

md.pattern(ecopols) #the variables with missing values:

mcar_test(data=ecopols)
```

### Solar : Mifa for new eco-pol value scale

@@

miecopols <- mifa(data= ecopols,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=5,
                n_pc= 1:2,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

miecopols

@@

print.psych(ecopolfits, sort= TRUE, cut= 0.4)

@@

### Solar 2 : only charcateristics of tech

@@

str(ecopols2)
md.pattern(ecopols2) #the variables with missing values:

mcar_test(data=ecopols2)
```

### SOLAR2 : Mifa for new eco-pol value scale

@@

miecopols2

@@

print.psych(ecopolfits2, sort= TRUE, cut= 0.4)

@@

@@

secopol2final <- data.frame(factor.scores(ecopols2means[, 1:10], ecopolfits2)$scores)

@@

### Solar LMs
```{r}

@@

solar2lm <- lm(Risky_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian , data = n2allfinal)

summary(solar2lm)

netsolar2lm <- lm(Netben_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(netsolar2lm)

bensolar2lm <- lm(Ben_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(bensolar2lm)

@@

### Solar: Mifa with CFA

```{r}

@@

secopol_cfa <- cfa(ecopols_2fa, data = miecopols$cov_combined, std.lv = TRUE)
summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)

@@

# COAL : MAR condition and missing data pattern

@@

@@

md.pattern(ecopolc) #the variables with missing values:

mcar_test(data=ecopolc)
```

# Coal : Mifa for new eco-pol value scale

@@

miecopolc

ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 3, rotate = "varimax")

print.psych(ecopolfitc, sort= TRUE, cut= 0.4)

@@

# COAL2 : only charcateristics of tech

@@

md.pattern(ecopolc2) #the variables with missing values:

mcar_test(data=ecopolc2)
```

# Coal2 : Mifa for new eco-pol value scale

@@

miecopolc2 <- mifa(data= ecopolc2,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=5,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

miecopolc2

@@

print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)

@@

```{r}

cor.plot(ecopolc %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
```

# Coal: Mifa with CFA

```{r}

@@

# EXTRA

## Kahan: factor scores from 1st imputed dataset
```{r, echo=FALSE}

>>>>

---
title: "models with mice"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
    keep_md: yes
    latex_engine: xelatex
geometry: "left=0.5cm,right=0.5cm,top=0.5cm,bottom=0.5cm"
header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
html_document:
  toc: yes
  toc_depth: '2'
  df_print: paged
---

@@

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(Hmisc))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(naniar))
suppressPackageStartupMessages(library(mice))
library(officer)
library(magrittr)
library(kableExtra)

@@

#sum(is.na(codedmodule2)) # 13 % of the data is missing.

@@

# Plot the graph with facets for each Question
#ggplot(WBques_summary, aes(x = State, y = Proportion, fill = factor(Response, levels = rev(levels_defined)))) +
  #geom_bar(stat = "identity", position = "fill") +
  #scale_fill_manual(values = rev(colorsequence), name = NULL) +
  #facet_wrap(~ Question, scales = "free_y", ncol = 1) +
  #coord_flip() +
  #labs(x = "State", y = "Proportion", title = "Proportion of Responses by State for Nuclear energy related questions") +
  #theme_minimal() +
  #theme(
    # Increase the size of the main title
    #plot.title = element_text(size = 16, face = "bold"),
    # Increase the size of the axis titles
    #axis.title = element_text(size = 14),
    # Increase the size of the facet strip text
    #strip.text.x = element_text(size = 12),
    # Adjust text angle for State labels if necessary
    #axis.text.y = element_text(angle = 0)
  #)

@@

# Print the combined plot
#grid::grid.newpage()
#grid::grid.draw(combined_plot)

@@

#n_acceptreject<- module2 %>%
                #dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")

#summary(n_acceptreject)
```

@@

#str(formice)
#summary(formice)

@@

#sum(is.na(formice))

@@

#str(kahanall)

#md.pattern(kahanall) #the variables with missing values: K_SHARM K_IPROTECT K_IPRIVACY K_SPROTECT K_SLIMCHOI K_IINTRFER K_HEQUAL K_HREVDIS1

#mcar_test(data=kahanall) # p values is less than 0.05 - the condition for MCAR is not met

@@

# "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SHARM_MAR"
#MARkahan %>% 
  #missing_compare(dependent, explanatory) %>% 
    #knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        #caption = "comparisons between values of responders (Not missing) and 
        #non-responders (Missing) on the K_SHARM variable.")

@@

@@

#print.psych(fit, sort= TRUE, cut= 0.4)

@@

#print.psych(kahanfit4, sort= TRUE, cut= 0.4)

@@

\blandscape
\newpage

@@

#kahan_imp <- mice(kahanall, m =5, maxit =30,  seed = 427, print = FALSE)

#kahan_imp$chainMean

@@

kahanallscores <- mice::complete(mice::mice(kahanall, m = 50, seed = 427, print = FALSE), "broad")

@@

#str(kahanallscores)

@@

## corelation table
```{r, echo = FALSE}

#cor(nkahanall)

#before mice 
#cor.plot(kahanall %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))

#after mice

#cor.plot(nkahanall)

#cov(nkahanall)

@@

#nkahanfinal %>%
  #ggplot(aes(MR1, MR2))+
  #geom_count(aes(color = ..n.., size = ..n..))+
  #guides(color = 'legend')+
  #geom_hline(yintercept=0, colour="black", lwd=0.5)+
  #geom_vline(xintercept=0, colour="black", lwd=0.5)+
  #labs(x = "Hierarchy -Egalitarianism", y = "Individualism - Communitarianism")+
  #ylim(-2,3)+
  #xlim(-2,3)+
  #theme_minimal() 
```

@@

#md.pattern(ecopoln) #the variables with missing values: PRIDENUCLEAR PROSPERNUCLEAR JOBSNUCLEAR HEALTHNUCLEAR BEAUTYNUCLEAR POLLUTENUCLEAR DISPLACENUCLEAR RELYNUCLEAR

#mcar_test(data=ecopoln) # p values is less than 0.76 - the condition for MCAR is met

@@

# JOBSNUCLEAR
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "JOBSNUCLEAR_MAR"
#MARecopol %>% 
  #missing_compare(dependent, explanatory) %>% 
    #knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        #caption = "comparisons between values of responders (Not missing) and 
        #non-responders (Missing) on the JOBSNUCLEAR variable.")

@@

@@

#print.psych(ecopolfit2, sort= TRUE, cut= 0.4)

@@

\newpage
## Radar map

@@

#nrow(ecopolfit2$loadings)

@@

```{r, echo=FALSE, fig.width=8, fig.height=6, out.width='100%', out.height='100%'}
library(fmsb)

@@

#Statenacheck1 <- allformice %>%
  #na.omit()%>%
  #dplyr::select(State)

#summary(Statenacheck1)
```

@@

#nuclear_missing <- allformice %>% dplyr::select(Risky_Nuclear,Uppercaste, Male, Hindu, urban_rural, Age, State)%>%
 #na.omit()

#summary(nuclear_missing)

@@

#summary(nuclearfinal)
#summary(nuclearfinal2)
#summary(nuclearfinal3)
#summary(nuclearfinal4)

@@

#print(aic_values)

@@

#print(bic_values)

@@

#cor.plot(nforcor)
```

@@

#summary(nuclearinterac)

@@

\newpage
\blandscape
# Stargazer : all LMs

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(nuclearfinal, nuclearfinal2, nuclearfinal3, nuclearfinal4, nuclearinterac,
          title = "Table 6: 5 linear models: Perceived Risk of Nuclear Energy",
          type = "latex"
)
cat("\\endgroup")

@@

\elandscape

# Paper 2

## NUCLEAR

@@

ecopoln2 <- formice1 %>%
  dplyr::select(DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
    RELYNUCLEAR, age, urban_rural, gender, caste, religion, State
  )

#str(ecopoln2)
#md.pattern(ecopoln2) #the variables with missing values:

#mcar_test(data=ecopoln2)
```

## Mifa: only charcateristics of tech

@@

miecopol2 <- mifa(data= ecopoln,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion", DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION),
                m=50,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 429,)

ecopolfitn2 <- psych::fa(miecopol2$cov_combined, nfactors = 2, rotate = "varimax")
print.psych(ecopolfitn2, sort= TRUE, cut= 0.4)

@@

ecopoln2scores <- ecopoln2scores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State",    "DECISIONDECEN", "DECISIONCEN", "INDUSTRYSMALL", "INDUSTRYLARGE","ECONOMYLOCAL", "ECONOMYGLOBAL", "ENVOVERDEV","DEVOVERENV", "OWNERPVT", "OWNERPUB","OWNERREG", "OWNERNOREG", "WEALTHLIM", "MECHANISATION"))))

@@

### LMs : characteristics of tech

@@

nuclear2lm <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu +Age + urban_rural+ State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

#summary(nuclear2lm)

netnuclear2lm <- lm(Netben_Nuclear ~ Uppercaste + Male + Hindu +Age + urban_rural+ State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

#summary(netnuclear2lm)

bennuclear2lm <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu +Age+ urban_rural + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

#summary(bennuclear2lm)

\newpage

### Stargazer : characteristics of tech

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(nuclear2lm,  bennuclear2lm, netnuclear2lm,
          title = "",
          type = "latex"
)
cat("\\endgroup")

###  LMs : Nuclear all eco-pol

allformicefinal2 <- allformicefinal%>%mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
         Netben_Solar = Ben_Solar - Risky_Solar,
         Netben_Coal = Ben_Coal - Risky_Coal)

nuclearfinal4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal2)

bennuclear3lm <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal2)

#summary(bennuclear3lm)

netnuclear3lm <- lm(Netben_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = allformicefinal2)

#summary(netnuclear3lm)

@@

#md.pattern(ecopols) #the variables with missing values:

#mcar_test(data=ecopols)
```

### Solar : EFA Mifa all eco-pol

@@

miecopols <- mifa(data= ecopols,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=50,
                n_pc= 1:2,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

# EFA with mifa

@@

#print.psych(ecopolfits, sort= TRUE, cut= 0.4)

@@

### Solar 2 : EFA dataset : only charcateristics of tech

@@

#str(ecopols2)
#md.pattern(ecopols2) #the variables with missing values:

#mcar_test(data=ecopols2)
```

### SOLAR2 : EFA Mifa : chaaracteristics of tech

@@

@@

#print.psych(ecopolfits2, sort= TRUE, cut= 0.4)

@@

### only tech characters : Factor Scores (mean across all imputations)

@@

# factor scores : characteristics of technology 
secopol2final <- data.frame(factor.scores(ecopols2means[, 1:10], ecopolfits2)$scores)

@@

### LMs : only characteristics of technology

@@

solar2lm <- lm(Risky_Solar ~ Uppercaste + Male + Hindu +Age+ urban_rural + State + DevPride + SocialCosts + Egalitarian + Communitarian , data = n2allfinal)

#summary(solar2lm)

netsolar2lm <- lm(Netben_Solar ~ Uppercaste + Male + Hindu +Age + urban_rural+ State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

#summary(netsolar2lm)

bensolar2lm <- lm(Ben_Solar ~ Uppercaste + Male + Hindu +Age + urban_rural+ State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

#summary(bensolar2lm)

@@

\newpage 
### Stargazer : EFA characteristics of technology

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(solar2lm,  bensolar2lm, netsolar2lm,
          title = "",
          type = "latex"
)
cat("\\endgroup")

### Solar: Mifa with CFA (Pdevelop and Ndevelop)

# dataset with all eco-pol vars 
#miecopols

@@

secopol_cfa <- cfa(ecopols_2fa, data = miecopols$cov_combined, std.lv = TRUE)
#summary(secopol_cfa, fit.measure= TRUE, standardized = TRUE)

@@

\blandscape
\newpage

### Pretty Table: CFA solar

@@

# Extract parameter estimates
sparams <- parameterEstimates(secopol_cfa, standardized = TRUE)%>%
   slice(1:(n()-13))

sparams1 <- sparams %>%
  mutate(rhs = case_when(
  rhs == "DISPLACESOLAR" ~ "Solar energy is leading to displacement of people from their land",
  rhs == "BEAUTYSOLAR" ~ "Solar energy spoils the natural beauty of the landscape",
  rhs == "POLLUTESOLAR" ~ "Solar energy increases pollution of air/water/land",
  rhs == "HEALTHSOLAR" ~ "Solar energy poses a great risk to the health of people living around it",
  rhs == "JOBSSOLAR" ~ "Solar energy will bring jobs to the local community",
  rhs == "PRIDESOLAR" ~ "I would be proud if my community used Solar energy",
  rhs == "NPRIDESOLAR" ~ "Solar energy is a mark of pride for our nation",
  rhs == "DEVSOLAR" ~ "Solar energy pushes forward the country's development",
  rhs == "PROSPERSOLAR" ~ "Solar energy brings economic prosperity to the surrounding regions",
  rhs == "RELYSOLAR" ~ "I don't like the idea that I have to rely on the government for electricity from Solar energy",
  rhs == "INDUSTRYSMALL" ~ "Large corporations are destroying the local industries in India and benefiting only a handful of people",
  rhs == "OWNERREG" ~ "Regardless of ownership, the government should pass strong regulations and implement them",
  rhs == "MECHANISATION" ~ "Rapid mechanization of work is taking away jobs from workers in this country",
  rhs == "ENVOVERDEV" ~ "Polluting industries that spoil the environment should be shut down even if it costs people their jobs",
    TRUE ~ as.character(rhs)
  )) %>%
  dplyr::select(!c(lhs,op, std.nox)) %>%
    rename(
    "Items" = rhs,
    "Loadings" = est,
    "Standard Error" = se,
    "zvalue" = z) %>%
  mutate(across(c("Loadings", "Standard Error", "zvalue"), round, 3))

sparams1$Scale <- NA
sparams1$Scale[1:5] <- "People Centered Development"
sparams1$Scale[6:10] <- "Nationalist Development"
sparams1 <- sparams1[, c("Scale", setdiff(names(sparams1), "Scale"))]

CFAsolar <- knitr::kable(sparams1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on eco-pol scale (Solar Energy)") %>%
  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
  column_spec(column = 2, width = "4cm")

# Print the table
CFAsolar %>%
  landscape()

\elandscape
### CFA SCORES (mean across all imputations)

ecopolallscoress2 <- mice::complete(mice::mice(ecopols, m = 50, seed = 429, print = FALSE), "broad")

ecopolallscoress2 <- ecopolallscoress2 %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))

secopol2 <- ecopolallscoress2 %>%
  rowwise() %>%
  mutate(DEVSOLAR_mean = mean(c_across(starts_with("DEVSOLAR"))),
         PROSPERSOLAR_mean = mean(c_across(starts_with("PROSPERSOLAR"))),
         NPRIDESOLAR_mean = mean(c_across(starts_with("NPRIDESOLAR"))),
         PRIDESOLAR_mean = mean(c_across(starts_with("PRIDESOLAR"))),
         JOBSSOLAR_mean = mean(c_across(starts_with("JOBSSOLAR"))),
         ECONOMYGLOBAL_mean = mean(c_across(starts_with("ECONOMYGLOBAL"))),
         WEALTHLIM_mean = mean(c_across(starts_with("WEALTHLIM"))),
         INDUSTRYLARGE_mean = mean(c_across(starts_with("INDUSTRYLARGE"))),
         DECISIONCEN_mean = mean(c_across(starts_with("DECISIONCEN"))),
         MECHANISATION_mean = mean(c_across(starts_with("MECHANISATION"))),
         OWNERNOREG_mean = mean(c_across(starts_with("OWNERNOREG"))),
         INDUSTRYSMALL_mean = mean(c_across(starts_with("INDUSTRYSMALL"))),
         DEVOVERENV_mean = mean(c_across(starts_with("DEVOVERENV"))),
         OWNERPVT_mean = mean(c_across(starts_with("OWNERPVT"))),
         RELYSOLAR_mean = mean(c_across(starts_with("RELYSOLAR"))),
         BEAUTYSOLAR_mean = mean(c_across(starts_with("BEAUTYSOLAR"))),
         HEALTHSOLAR_mean = mean(c_across(starts_with("HEALTHSOLAR"))),
         POLLUTESOLAR_mean = mean(c_across(starts_with("POLLUTESOLAR"))),
         DISPLACESOLAR_mean = mean(c_across(starts_with("DISPLACESOLAR"))),
         ENVOVERDEV_mean = mean(c_across(starts_with("ENVOVERDEV"))),
         OWNERPUB_mean = mean(c_across(starts_with("OWNERPUB"))),
         OWNERREG_mean = mean(c_across(starts_with("OWNERREG"))),
         DECISIONDECEN_mean = mean(c_across(starts_with("DECISIONDECEN"))),
         ECONOMYLOCAL_mean = mean(c_across(starts_with("ECONOMYLOCAL")))
  ) %>%
  ungroup()%>%
  dplyr::select(contains("_mean")) %>%
   rename_with(~ gsub("_mean$", "", .x))

solarCFAscores <- predict(secopol_cfa, newdata = secopol2)

cfasolarscoresfinal  <- cbind(formice1, solarCFAscores, nkahanfinal) %>%
      rename(Egalitarian = MR1, Communitarian = MR2)%>%mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
         Netben_Solar = Ben_Solar - Risky_Solar,
         Netben_Coal = Ben_Coal - Risky_Coal)

###  CFA LMs: Risk, Ben, Net Ben X Pdevelop Ndevelop

solarfinal4 <- lm(Risky_Solar ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = cfasolarscoresfinal)

#summary(solarfinal4)

bensolar3lm <- lm(Ben_Solar ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = cfasolarscoresfinal)

#summary(bensolar3lm)

netsolar3lm <- lm(Netben_Solar ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Egalitarian + Pdevelop + Ndevelop, data = cfasolarscoresfinal)

#summary(netsolar3lm)

### Stargazer : CFA Pdevelop Ndevelop

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(solarfinal4,  bensolar3lm, netsolar3lm,
          title = "",
          type = "latex"
)
cat("\\endgroup")

## COAL

### Coal:MAR condition and missing data pattern
```{r, echo=FALSE}

@@

#md.pattern(ecopolc) #the variables with missing values:

#mcar_test(data=ecopolc)
```

###  Mifa: EFA all ecopol

@@

# EFA With mifa - all ecopol vars for coal
ecopolfitc <- psych::fa(miecopolc$cov_combined, nfactors = 3, rotate = "varimax")

#print.psych(ecopolfitc, sort= TRUE, cut= 0.4)

@@

### Dataset: only tech characters

@@

#md.pattern(ecopolc2) #the variables with missing values:

#mcar_test(data=ecopolc2)
```

### EFA Mifa: only tech characters

@@

miecopolc2 <- mifa(data= ecopolc2,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=50,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

@@

#print.psych(ecopolfitc2, sort= TRUE, cut= 0.4)

@@

#cor.plot(ecopolc %>% dplyr::select(-c("age", "gender", "caste", "State", "urban_rural", "religion")))
```

### CFA Mifa: Pdevelop n Ndevelop

@@

\blandscape

\newpage
### Pretty Table
